The bhsdtr package: flexible bayesian inference for hierarchical or non-hierarchical equal variance normal Signal Detection Theory models with or without ratings.

### 2017-11-03 inst/preprint/luxsdt.tex
added single-criterion SDT test

In the study in question the response was originally encoded as
accuracy and rating, so the first step was to create an appropriate
response variable using the \texttt{combined\_response} function. This
function needs three variables, one encoding the stimulus class, one
encoding the rating (as an integer) and one encoding decision
accuracy. This step is required only if ratings are available and the
combined response variable is not already present in the data. In the
$K=2$ case the combined response variable is simply the binary
classification decision.

@@

>>>>

In the study in question the response was originally encoded as
accuracy and rating, so the first step was to create an appropriate
response variable using the \texttt{combined\_response} function. This
function needs three variables, one encoding the stimulus class, one
encoding the rating (as an integer) and one encoding decision
accuracy.

@@

This step is required only if ratings are available and the combined
response variable is not already present in the data. In the single
criterion case the combined response variable is simply the binary
classification decision. To fit the single-criterion SDT model to this
dataset the code above would have to be replaced with the following:

\begin{lstlisting}{language=R}
  gabor$resp = combined_response(gabor$stim, accuracy = gabor$acc)
\end{lstlisting}
